Untrusted B2B Collaboration using the Blockchain

### 2018-07-09 paper/paper.tex
Preliminary intro
Start related work

\section{Preliminary}

\subsection{Orchestractions and Choreographies}

@@

\section{Related Work}

summarize untrusted paper
summarize Caterpillar
acknowledge their Work
display the shortcomings

maybe also include Blockchain here?

>>>>

\section{Preliminary}
In the following section we present concepts and technologies that are related to our concept.

\subsection{Orchestrations and Choreographies}
A work by Weber et. al \citep{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations. They use a smart contract that all parties of a business process communicate with.

@@

\subsection{Prior Work on Business Processes on the Blockchain}
%summarize untrusted paper
%summarize Caterpillar
%acknowledge their Work
%display the shortcomings
